Ore Polynomials in Sage

### 2013-06-14 paper/main.tex

\begin{sageexample}
  sage: load("ore_algebra.py", "guessing.py", "ore_operator.py");  #### TO BE FIXED ####
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\section{Guessing}\label{sec:5}

[[CITE RUBEY.]]

Guessing is one of the most popular features of software packages like gfun.  It
is a technique for detecting patterns in sequences of numbers, which is often
used in combinatorics. The basic idea is simple. If we are given a finite array
of numbers, though of as the first terms of an infinite sequence, we may want to
know whether this sequence satisfies a recurrence. The algorithm behind a
guessing engine searches for small equations matching the given data.
Generically, no such equations exist, so if some are found, it is fair to
``guess'' that they are in fact valid equations for the whole infinite sequence.
=======
\subsection{Guessing}

Guessing is, in some sense, the reverse operation of \verb|to_list|. It is one
of the most popular features of packages like gfun, and there are even some
special purpose packages dedicated to this technique~\cite{kauers09a,hebisch11}.
The basic idea is simple. If we are given a finite array of numbers, thought of
as the first terms of an infinite sequence, we may want to know whether this
sequence satisfies a recurrence. The algorithm behind a guessing engine searches
for small equations matching the given data.  Generically, no such equations
exist, so if some are found, it is fair to ``guess'' that they are in fact valid
equations for the whole infinite sequence.
>>>>>>> manuel/master

>>>>

\begin{sageexample}
  sage: from ore_algebra import *
  sage: R.<x> = PolynomialRing(ZZ); A.<Dx> = OreAlgebra(R)
  sage: A
  sage: A.random_element()
  sage: Dx*x
  sage: B.<Sx> = OreAlgebra(R)
  sage: B
  sage: Sx*x
\end{sageexample}

@@

\subsection{Guessing}

Guessing is, in some sense, the reverse operation of \verb|to_list|. It is one
of the most popular features of packages like gfun, and there are even some
special purpose packages dedicated to this technique~\cite{kauers09a,hebisch11}.
The basic idea is simple. If we are given a finite array of numbers, thought of
as the first terms of an infinite sequence, we may want to know whether this
sequence satisfies a recurrence. The algorithm behind a guessing engine searches
for small equations matching the given data.  Generically, no such equations
exist, so if some are found, it is fair to ``guess'' that they are in fact valid
equations for the whole infinite sequence.
